### 2017-07-07 paper.tex
Adding acknowledgments.
Closes #34.

>>>>

\subsection*{Acknowledgments}

We are grateful to everyone who provided feedback on this paper,
including
James Baker,
Nathan Moore,
Pariksheet Nanda,
Tom Pollard,
Byron Smith,
and Andrew Walker.
We are also grateful to the hundreds of people who have contributed to
Programming Historian, Data Carpentry, Software Carpentry, and Library Carpentry
over many years.
